Chemically Selective Transport in a Cross-linked H\textsubscript{II} Phase Lyotropic Liquid Crystal Membrane

### 2019-05-07 Ben_Manuscripts/transport/Draft.tex
Updates in response to comments

  %MRS2: rephrasing
  Sodium coordinates with both water and carboxylate moieties from the head groups in the pores.
  Sodium coordinates with 3.4 water molecules in bulk solution (see 
  Section~\ref{method:coordination}), but on average in the pores,
  coordinates with 1.7 water molecules in the 10 wt\% system and 1.2 water
  molecules in the 5 wt\% system. The sodium ions additionally coordinate with 1 carboxylate group in the 10 wt\% water
  system and 0.8 carboxylate groups in the 5 wt\% water system. This behavior likely
  slows the motion of the sodium ions considerably compared to bulk water.
  %MRS2: is one sodium per carboxylate group correct?
  % Assuming only one sodium per carboxylate group, the numbers were multiplied by 2
  % since the averages were divided by 800 instead of 400

  In the 10 wt\% water system, water molecules that spend the majority of 
  their time in the distal tail region move significantly slower than those
  close to the pore center. In Figure~\ref{fig:water_msd_comparison}, we 
  constructed the MSD curves based on water molecules that spent $>$ 95\% of their
  time outside the distal tail region. If we instead restrict our calculation to
  water molecules that spend $>$ 95\% of their time \textit{in} the distal tail region, 
  the MSD of distal tail water decreases 8-fold from 59.6 to 8.2 nm$^2$.

@@

  %MRS2: trying something else to emphasize what we are trying to do.  Can you add a bit more detail so it's not just slowing up or speeding solutes, but slowing or speeding up solutes of a particular type?  We can emphasize chemical selectivity . . . 
  %mitigate or enhance their effect on   solute MSDs.   
  %BJC3: gave it a try
  Based on these trapping mechanisms, we may be able to suggest modifications
  that can be made to monomers that will modulate their effect on specific 
  solute MSDs in order to make transport even more selective for particular 
  solutes. Since solutes move slowly while entangled among the monomer tails, 
  one can try to design monomers that better control the partition of solutes
  between the pore and tail region. For example, removal of the ether linkages between the
  head groups and the monomer tails will decrease the stability of polar 
  molecules near the head groups. Solutes that spend a large fraction of their 
  time in the tails, such as butanol with its high hydrophilic character, could
  exhibit higher permeabilities from these types of changes. Alternatively, one
  can focus on designing head groups with varying hydrogen bonding capabilities.
  One can increase the number of hydrogen bonding sites on the head groups in 
  order to trap solutes like sugars that have many hydroxyl groups, or decrease
  the number of hydrogen bond sites to trap less. Finally, one can attempt to control 
  the degree to which solutes coordinate with counterions. Changing the size
  and valence of the counterion may offer some interesting behavior. Higher
  valence counter ions will bind more strongly to solutes which may be a useful
  way to trap solutes like urea with carbonyl groups. These hypotheses remain to be 
  tested in future simulations of new monomers.

  The findings here are likely too complex to point towards a clear design of an 
  optimal LLC membrane for a particular separation. This work does demonstrate
  that a large range of solute-membrane interactions resulting from the chemically
  complex and inhomogeneous LLC membrane structure and the varying chemical 
  functionality of the solutes themselves gives rise to an immense diversity of
  transport behavior. This behavior suggests that a large range of chemical 
  selectivities may be possible in self-assembled nanoporous membranes. Atomistic
  modeling gives us the opportunity to observe these interactions at the molecular
  scale, at least approximately, so that we can think more critically about 
  nanostructured membrane design.

>>>>

  Sodium coordinates with both water and carboxylate moieties from the head
  groups in the pores. Sodium coordinates with 3.4 water molecules in bulk 
  solution (see Section~\ref{method:coordination}), but on average in the pores,
  coordinates with 1.7 water molecules in the 10 wt\% system and 1.2 water
  molecules in the 5 wt\% system. The sodium ions additionally coordinate with
  1 carboxylate group in the 10 wt\% water system and 0.8 carboxylate groups 
  in the 5 wt\% water system. This behavior likely slows the motion of the 
  sodium ions considerably compared to bulk water.
  %MRS2: is one sodium per carboxylate group correct?
  %BJC3: yes, if sodium within cutoff of both oxygens, it is only counted once.
  % Assuming only one sodium per carboxylate group, the numbers were multiplied by 2
  % since the averages were divided by 800 instead of 400

  In the 10 wt\% water system, water molecules that spend the majority of 
  their time in the distal tail region move significantly slower than those
  close to the pore center. In Figure~\ref{fig:water_msd_comparison}, we 
  constructed the MSD curves based on water molecules that spent $>$ 95\% of their
  time outside the distal tail region. If we instead restrict our calculation to
  water molecules that spend $>$ 95\% of their time \textit{in} the distal tail region, 
  the MSD of water is about 8 times lower, decreasing from 59.6 to 8.2 nm$^2$.

@@

  %MRS2: trying something else to emphasize what we are trying to do.  Can you add a bit more detail so it's not just slowing up or speeding solutes, but slowing or speeding up solutes of a particular type?  We can emphasize chemical selectivity . . . 
  %mitigate or enhance their effect on   solute MSDs.   
  %BJC3: gave it a try. Broke into paragraphs
  Based on these trapping mechanisms, we may be able to suggest modifications
  that can be made to monomers that will modulate their effect on specific 
  solute MSDs in order to make transport even more selective for particular 
  solutes.

  Since solutes move slowly while entangled among the monomer tails,
  and since more than half of the solutes studied spend at least 40\% of their
  time in the tails, one can try to design monomers that better control the 
  partition of solutes between the pore and tail region. Solutes move into 
  the tails due both to their size and hydrophilic character. One may be 
  able to contain solutes, even small ones like methanol, by increasing
  the density of monomers close to the head groups through incorporation of 
  cross-linkable groups in the vicinity. Alternatively, removal of the ether
  linkages between the head groups and the monomer tails may decrease the 
  stability of any of the molecules we studied near the head groups and 
  force them to spend more time within the pore.

  %Solutes that spend a large fraction of their 
  %time in the tails, such as butanol with its high hydrophilic character, could
  %exhibit higher permeabilities from these types of changes.

  One can instead focus on designing head groups with varying hydrogen bonding
  capabilities. Increasing the number of hydrogen bonding sites on the head 
  groups may enhance the membrane's ability to trap solutes like sugars that 
  have many hydroxyl groups. Conversely, one can decrease the number of hydrogen
  bond sites, or replace them with weaker hydrogen bonding atoms like nitrogen, to
  trap less. In contrast to the system studied here, one can design the head 
  groups so they can donate hydrogen bonds, which can enhance entrapment of 
  solutes like acetone that can only accept hydrogen bonds.

  Finally, one can attempt to control the degree to which solutes coordinate
  with counterions. Increasing the valence of the counterions may cause them
  to bind more strongly to solutes which may be a useful way to trap 
  carbonyl-containing solutes like urea for longer periods of time. Of course,
  an increased valence would require proportionately less total counter ions
  to balance the system charge which could result in the opposite effect. One
  could also design the head groups so that counterions are negatively charged
  which may eliminate their interaction with most solutes.

%  
%  These hypotheses remain to be tested in future simulations of new
%  monomers.

  The findings here are likely too complex to point towards a clear design of an 
  optimal LLC membrane for a particular separation. This work does demonstrate
  that there is a large range of solute-membrane interactions resulting from the
  chemically complex and inhomogeneous LLC membrane structure. The varying 
  chemical functionality of the solutes themselves gives rise to an immense diversity of
  transport behavior. This behavior suggests that a large range of chemical 
  selectivities may be possible in self-assembled nanoporous membranes. Atomistic
  modeling gives us the opportunity to observe these interactions at the molecular
  scale, at least approximately, so that we can think more critically about 
  nanostructured membrane design.
